### 2023-08-14 appendix.tex
up

As mentionned in Section~\ref{section VASS}
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable. This stems from the fact that there are simple conditions in VASS that ensure neither {\sc $k$-resilience }  nor {\sc Bounded resilience} hold.
Restricting oneself to the case where these conditions are not met simplifies the problem.

>>>>

As mentionned in Section~\ref{section VASS},
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable. This stems from the fact that there are simple conditions in VASS that ensure neither {\sc $k$-resilience }  nor {\sc Bounded resilience} hold.
Restricting oneself to the case where these conditions are not met simplifies the problem.
Let us provide a more detailed decidability proof here.
